Responses to the Reviewers' Comments

### 2024-11-01 Response/Paper_Res.tex
Rev_V7.5

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods while providing a substantial improvement by 37.1\%\,--\,29.8\% in average QoE compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and the distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

	\color{blue}
	\item \textcolor{blue}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. This method is designed for distributed computation offloading in a queuing-based MEC environment.}

@@

@@

(c) Indeed, compared to \cite{yang2018distributed}, QECO improves the number of completed tasks by 14.4\% while at the same time reduces task delay and energy consumption by 9.2\% and 6.3\%, respectively. These together contribute to a significant improvement of 37.1\% in average QoE compared to \cite{yang2018distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows.

@@

@@

@@

				Simulation results reveal that compared to the state-of-the-art existing work, QECO increases the number of completed tasks by 11.2\%\,--\,14.4\%, while simultaneously reducing task delay and energy consumption by 11.7\%\,--\,9.2\% and 9.8\%\,--\,6.3\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of at least 29.8\%\,--\,37.1\% compared to several existing algorithms.
}

@@

	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.

@@

				\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods while providing a substantial improvement by 37.4\%\,--\,29.8\% in average QoE compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and the distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

			\dots
	}}
\end{my}\vspace{6mm}

@@

\,\,\,\,The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement \cite{wang2017qoe}, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time \cite{wang2019intelligent}, \cite{mehrabi2019energy}. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra-power-saving. 
Based on the system model, we first calculate task delay and energy consumption and then represent the associated cost and QoE function accordingly.

@@

	\begin{my}{1cm}{1cm}
		\rev{In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. 
			\textcolor{blue}{Based on the previous sample experiences $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (in steps 11-21 of Algorithm ~\ref{alg:cap2}) to keep parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ update for the MD's \textit{UpdateRequest}}. The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:\\ \dots}
	\end{my}

@@

			\,\,\,\, The algorithm's source code is available at \cite{QECO}

>>>>

\,\,\,\,
In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{red}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading in uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{red}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users. \vspace{3mm}

\,\,\,\,
Our main contributions are summarized as follows:

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{red}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies.} We also analyze the training convergence and computational complexity of the proposed algorithm.

	\item \textit{Performance Evaluation:} \textcolor{red}{We conduct comprehensive experiments to evaluate QECO’s performance and training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs while taking the dynamic workloads at ENs into consideration. In particular, it converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

	\color{blue}
	\item \textcolor{red}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. DCDRL is designed for distributed computation offloading in a queuing-based MEC environment.}

@@

\dots \color{black}

@@

(c) Indeed, compared to \cite{yang2018distributed}, QECO improves the number of completed tasks by 14.4\% while at the same time reduces task delay and energy consumption by 9.2\% and 6.3\%, respectively. These together contribute to a significant improvement of 37.1\% in average QoE compared to \cite{yang2018distributed}. To clarify the improvement obtained by QECO, we have revised the abstract, Section I, and Section VI as follows. \vspace{4mm}

@@

		\begin{my}{1cm}{1cm}
	\rev{\color{black}

\begin{abstract}

				In the realm of mobile edge computing (MEC), efficient computation task offloading plays a pivotal role in ensuring a seamless quality of experience (QoE) for users. Maintaining a high QoE is paramount in today's interconnected world, where users demand reliable services. This challenge stands as one of the most primary key factors contributing to handling dynamic and uncertain mobile environment. In this study, we delve into computation offloading in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance. We formulate the computation task offloading problem as a Markov decision process (MDP) to maximize the long-term QoE of each user individually. We propose a distributed QoE-oriented computation offloading (QECO) algorithm based on deep reinforcement learning (DRL) that empowers mobile devices to make their offloading decisions without requiring knowledge of decisions made by other devices. Through numerical studies, we evaluate the performance of QECO. \textcolor{red}{
					Simulation results reveal that compared to the state-of-the-art existing works, QECO increases the number of completed tasks by up to 14.4\%, while simultaneously reducing task delay and energy consumption by 9.2\% and 6.3\%, respectively. Together, these improvements align with user preferences, resulting in a significant average QoE enhancement of 37.1\%. This substantial improvement is achieved by accurately accounting for user dynamics and edge server workloads while making intelligent offloading decisions. This highlights QECO's effectiveness in enhancing MEC systems.}

	\end{abstract}

}

	\setcounter{section}{0}

@@

\section{Introduction} 
\dots

\,\,\,\,
Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. \textcolor{red}{In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the MEC systems.}\vspace{3mm}

\,\,\,\,
To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. \textcolor{red}{However, the traditional RL methods are not efficient to  handle  environments with high-dimensional state  spaces. Deep reinforcement learning (DRL) combines  traditional RL  with  deep  neural  networks  to  intelligently respond to the unknown and dynamic system when addressing the limitations of RL-based algorithms. Despite these advancements, task offloading still faces significant challenges in real-world scenarios with multiple MDs and ENs. In such scenarios, it is essential for MDs to make offloading decisions independently  without prior knowledge of other MDs’ tasks and offloading models. However,  existing works fail to adequately address this challenge. In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly estimate the QoE value and address the user demands and requirements. Although deep Q-networks (DQN) offer a valuable tool, a more comprehensive approach is required to accurately estimate the QoE while addressing the aforementioned challenges in practical scenarios where global information is limited.}\vspace{3mm}

\,\,\,\,
In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{red}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading in uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
\textcolor{red}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users. \vspace{3mm}

\,\,\,\,
Our main contributions are summarized as follows:

\begin{itemize}
	\item \textit{Task Offloading Problem in the MEC System:} \textcolor{red}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }

	\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies.} We also analyze the training convergence and computational complexity of the proposed algorithm.

	\item \textit{Performance Evaluation:} \textcolor{red}{We conduct comprehensive experiments to evaluate QECO’s performance and training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs while taking the dynamic workloads at ENs into consideration. In particular, it converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

}

@@

	\textcolor{red}{	\,\,\,\, In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly estimate the QoE value and address the user demands and requirements. }

@@

		\,\,\,\,
		Efficient task offloading in MEC is a complex optimization challenge due to the dynamic nature of the network and the variety of MDs and servers involved \cite{jiang2019toward} \cite{TNSE-WU-24}. In particular, determining the optimal offloading strategy, scheduling the tasks, and selecting the most suitable EN for task offloading are the main challenges that demand careful consideration. \textcolor{red}{In addition to the dynamic network changes, the uncertain requirements and sensitive latency properties of computation tasks pose nontrivial challenges that can significantly impact the MEC systems.}\vspace{3mm}

		\,\,\,\,
		To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives. \textcolor{red}{However, the traditional RL methods are not efficient to  handle  environments with high-dimensional state  spaces. Deep reinforcement learning (DRL) combines  traditional RL  with  deep  neural  networks  to  intelligently respond to the unknown and dynamic system when addressing the limitations of RL-based algorithms. Despite these advancements, task offloading still faces significant challenges in real-world scenarios with multiple MDs and ENs. In such scenarios, it is essential for MDs to make offloading decisions independently  without prior knowledge of other MDs’ tasks and offloading models. However,  existing works fail to adequately address this challenge. In addition, QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly estimate the QoE value and address the user demands and requirements. Although deep Q-networks (DQN) offer a valuable tool, a more comprehensive approach is required to accurately estimate the QoE while addressing the aforementioned challenges in practical scenarios where global information is limited.}\vspace{3mm}

		\,\,\,\,
		In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system performance.   \textcolor{red}{We propose a distributed QoE-oriented computation offloading (QECO) algorithm to efficiently handle task offloading in uncertain loads at ENs.} This algorithm empowers MDs to make offloading decisions utilizing only locally observed information, such as task size, queue details, battery status, and historical workloads at the ENs. 
		\textcolor{red}{To capture the dynamic nature of the MEC environment, we employ the dueling double deep Q-network (D3QN), which is a refined improvement over standard DQN model. By integrating both double Q-learning \cite{van2016deep} and dueling network architectures \cite{wang2016dueling}, D3QN reduces overestimation bias in action-value predictions and more accurately distinguishes the relative importance of states and actions. We also incorporate long short-term memory (LSTM) \cite{hochreiter1997long} into our D3QN model to continuously estimate dynamic workloads at ENs. This enables MDs to effectively handle the uncertainty of the MEC environment, where global information is limited, and proactively adjust the offloading strategies to improve their long-term QoE estimation.} By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users. \vspace{3mm}

		\,\,\,\,
		Our main contributions are summarized as follows:

		\begin{itemize}
			\item \textit{Task Offloading Problem in the MEC System:} \textcolor{red}{ We consider queuing systems for MDs and ENs and formulate the task offloading problem as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). We aim to maximize the long-term QoE, which reflects the task completion rate, task delay, and energy consumption of MDs. Our problem formulation effectively utilizes the resources and properly handles the dynamic fluctuations of workload at ENs. }

			\item \textit{DRL-based Offloading Algorithm:} \textcolor{blue}{To solve the problem of long-term QoE maximization in highly dynamic mobile environments, we propose the QECO algorithm based on DRL, which empowers each MD to make offloading decisions independently, without prior knowledge of other MDs' tasks and offloading models. Focusing on the MD's QoE preference, our approach leverages D3QN and LSTM to prioritize and strike an appropriate balance between QoE factors while accounting for workload uncertainty at the ENs. QECO empowers MDs to anticipate the EN's load level over time, leading to more accurate offloading strategies.} We also analyze the training convergence and computational complexity of the proposed algorithm.

			\item \textit{Performance Evaluation:} \textcolor{red}{We conduct comprehensive experiments to evaluate QECO’s performance and training convergence against baseline schemes as well as two state-of-the-art existing works. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs while taking the dynamic workloads at ENs into consideration. In particular, it converges more quickly than vanilla DQN and DDQN methods. QECO also improves average QoE by 37.1\% and 29.8\% compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

	}

@@

\,\,\,\,\textcolor{red}{The QoE function reflects user satisfaction with task computation, whether using local or edge resources. QoE accounts for task completion rate, processing delay, and energy consumption. Each user may have unique QoE requirements~\cite{wang2017qoe}. Therefore, we define a multi-dimensional, adaptive structure to assess QoE, balancing these factors according to the MDs preferences, such as prioritizing reduced task delays or energy savings, which may vary over time~\cite{wang2019intelligent},~\cite{mehrabi2019energy}. To capture personalized QoE requirements, we define QoE as a weighted sum of the above factors. Each MD dynamically adjusts these weights to reflect the importance of different factors based on its energy modes, which are performance, power-saving, and ultra-power-saving modes. We now calculate task delay and energy consumption and then introduce the associated cost and QoE function.}

@@

		\dots \color{black}

		In particular, regarding experience $n$, the target-Q value $\hat{Q}_{i,n}^{\text{T}}$ represents the long-term QoE for action $\boldsymbol{a}_i(n)$ under state $\boldsymbol{s}_i(n)$. This value corresponds to the QoE observed in experience $n$, as well as the approximate expected upcoming QoE. 
			\textcolor{red}{Based on the set $\mathcal{N}$, the EN computes the vector $\hat{\mathbf{Q}}_i^{\text{T}} = (\hat{Q}^{\text{T}}_{i,n})_{n \in \mathcal{N}}$ and trains the MD's neural network (steps 11-21 of Algorithm~\ref{alg:cap2}) to update the parameter vector $\theta^{\text{E}}_i$ in $\textit{Net}_i^{\text{E}}$ for the next MD's \textit{UpdateRequest}.} The key idea of updating $\textit{Net}_i^{\text{E}}$ is to minimize the disparity in Q-values between $\textit{Net}_i^{\text{E}}$ and $\textit{Net}_i^{\text{T}}$, as indicated by the following loss function:

			\dots}
	\end{my}

@@

			\,\,\,\, \textcolor{red}{The algorithm's source code is available at \cite{QECO}}
